Stateless Model Checking with Data-Race Preemption Points

### 2015-11-15 pldi-16/paper.tex
anonymize acknowledgemence

Many thanks to Vaishaal Shankar, Haryadi Gunawi, and David A. Eckhardt for generously providing student implementations from Berkeley's, U. of Chicago's, and CMU's OS classes respectively.
Thanks to Wind River for the use of their simulator \simics.
Thanks to
% TODO: Post-double-blind-review
% Ji\v{r}\'{i} \v{S}im\v{s}a, John Wilkes, and
the anonymous PLDI reviewers for their helpful comments.
This work was supported in part by
the U.S. Army Research Office under grant number W911NF0910273.

>>>>

% TODO CAMREADY
{\em removed for double-blind review}
%Many thanks to Vaishaal Shankar, Haryadi Gunawi, and David A. Eckhardt for generously providing student implementations from Berkeley's, U. of Chicago's, and CMU's OS classes respectively.
%Thanks to Wind River for the use of their simulator \simics.
%Thanks to
%Ji\v{r}\'{i} \v{S}im\v{s}a, Joshua Wise, John Wilkes, and
%the anonymous PLDI reviewers for their helpful comments.
%This work was supported in part by
%the U.S. Army Research Office under grant number W911NF0910273.
